R Notebook

### 2020-02-10 src/comb-maxent.Rmd
updating binary predictions to max kap

@@

first bin the probabilities for cells inside the mcp

```{r bin probabilities}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)

  binprob <- function(x){
    ifelse(x > 0 & x < 0.1, 0.1,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.1 & x < 0.2, 0.2,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.2 & x < 0.3, 0.3,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.3 & x < 0.4, 0.4,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.4 & x < 0.5, 0.5,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.5 & x < 0.6, 0.6,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.6 & x < 0.7, 0.7,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.7 & x < 0.8, 0.8,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.8 & x < 0.9, 0.9,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.9 & x <= 1, 1,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
   # cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}
```

@@

for (m in 1:length(mthord)){
  for (b in 1:length(binlst)){
    mth <- mthord[m]
    bin <- binlst[b]
    # mth <- "dec"
    # bin <- 1
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_binned_", bin, "_avg.*asc"), full.names = TRUE)

@@

  }
  write.csv(stackstathigh, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_probbin_", bin, "_cellcount_bydepth_avg.csv"), row.names = FALSE)
  }
}

@@

based on Remi's code
```{r}
require(data.table)
require(purrr)
require(lubridate)
require(tidyverse)

>>>>

#binned probability cell count for the whole 3d space per month

```{r}
library(stringr)

#calculate no of cells in the 3D space
prob <- read.csv("../output/maxent/paper_plots/prob_by_depth/apr_dis_prob_cells.csv", header = TRUE) #just a randomly chosen dataset
t2 <- subset(prob, Probability == "0 - 0.09") #could have chosen any probability
tc <- sum(t2$total_cells) #173623

dislst <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "dis_prob_cells.csv", full.names = TRUE)
totlst <- list()
for (m in 1:length(dislst)){
  pr <- read.csv(dislst[m])
  mth <- str_sub(dislst[m], start = 44, end = 46)
  pr2 <- aggregate(pr$Cells, by=list(Category = pr$Probability), FUN = sum)
  pr2$percent <- (pr2$x/tc)*100
  pr2$month <- mth
  write.csv(pr2, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_cellprob_totals.csv"), row.names = FALSE)
  totlst[[m]] <- pr2
}

#then i just made a table manually in excel
```

@@

#max kappa thresholds

```{r}
binprob <- function(x){
  ifelse(x > 0 & x >= mk, 1,
  ifelse(x <= 0, 0, NA))
}

alst <- list.files("../output/maxent/models/test-comb/", pattern = "avgAIC.csv", full.names = TRUE)

for (f in 1:length(alst)){
  mth <- str_sub(alst[f], start = 35, end = 37)
  af <- read.csv(alst[f], header = TRUE)
  af <- tail(af, n = 1)
  mk <- af$test_maxkap

  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}

@@

for (m in 1:length(mthord)){
  for (b in 1:length(binlst)){
    mth <- mthord[m]
    bin <- binlst[b]
    # mth <- "dec"
    # bin <- 1
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_maxkap.*asc"), full.names = TRUE)

@@

  }
  write.csv(stackstathigh, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_", bin, "_cellcount_bydepth_avg.csv"), row.names = FALSE)
  }
}

@@

```
based on Remi's code
```{r}
require(data.table)
require(purrr)
require(lubridate)
require(tidyverse)

### 2020-02-10 src/testing_file.Rmd
updating binary predictions to max kap

library(sf)
library(purrr)
library(raster)
library(lubridate)
library(patchwork)
library(tidyverse)

@@

for(v in vars){
  if(v=='chl'){
   assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
            scale_fill_viridis(option="viridis", direction = -1, 
             #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+
           labs(title= "Chl \u03b1")+ #i added
           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  }else if(v=='o2'){
      assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
           scale_fill_viridis(option="viridis", direction = -1 , 
           #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+
           labs(title=paste0("Dissolved ", sapply(v, CapStr)))+ #i added

           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  }else if(v=='salinity'){
      assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
           scale_fill_viridis(option="viridis", direction = -1 , 
           #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "PSU", draw.ulim = FALSE, draw.llim = FALSE))+

           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           labs(title=sapply(v, CapStr))+ #i added
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  } else if(v=='temp'){
    assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
             geom_sf(data=s,fill='grey')+
             geom_raster(aes(x,y,fill=value))+
             geom_sf(data=mcp,fill="transparent")+
             scale_fill_viridis(option="viridis", direction = -1, 
             #scale_fill_distiller(palette="Spectral", direction=-1)+
             guide_colourbar(barwidth=0.5, title = "Kelvin", draw.ulim = FALSE, draw.llim = FALSE))+
             facet_wrap(~monthyear,nrow=4,strip.position = "right")+
             labs(title=sapply(v, CapStr))+ #i added
             theme_classic()+
             scale_x_continuous(breaks = seq(-70,-50,10))+
             theme(legend.position = "bottom",
                   axis.title.x=element_blank(),
                   axis.title.y=element_blank(),
                   axis.text.x=element_text(angle=45,vjust=1,hjust=1), strip.background = element_blank(),
                   strip.text.y = element_text(face = "bold")))
  }
}

@@

>>>>

library(sf)
library(purrr)
library(raster)
library(lubridate)
library(patchwork)
library(tidyverse)
library(viridis) #added by me

@@

for(v in vars){
  if(v=='chl'){
   assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
            scale_fill_viridis(option="viridis", direction = -1, limits = c(0.03, 4.5), 
             #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+
           labs(title= "Chl \u03b1")+ #i added
           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  }else if(v=='o2'){
      assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
           scale_fill_viridis(option="viridis", direction = -1, limits = c(207, 418) , 
           #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+
           labs(title=paste0("Dissolved ", sapply(v, CapStr)))+ #i added

           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  }else if(v=='salinity'){
      assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
           scale_fill_viridis(option="viridis", direction = -1, limits = c(22, 36), 
           #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "PSU", draw.ulim = FALSE, draw.llim = FALSE))+

           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           labs(title=sapply(v, CapStr))+ #i added
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  } else if(v=='temp'){
    assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
             geom_sf(data=s,fill='grey')+
             geom_raster(aes(x,y,fill=value))+
             geom_sf(data=mcp,fill="transparent")+  
             scale_fill_manual(col=blue2red(20), 
             #scale_fill_viridis(option="viridis", direction = -1, limits = c(270, 296),
             #scale_fill_distiller(palette="Spectral", direction=-1)+
             guide_colourbar(barwidth=0.5, title = "Kelvin", draw.ulim = FALSE, draw.llim = FALSE))+
             facet_wrap(~monthyear,nrow=4,strip.position = "right")+
             labs(title=sapply(v, CapStr))+ #i added
             theme_classic()+
             scale_x_continuous(breaks = seq(-70,-50,10))+
             theme(legend.position = "bottom",
                   axis.title.x=element_blank(),
                   axis.title.y=element_blank(),
                   axis.text.x=element_text(angle=45,vjust=1,hjust=1), strip.background = element_blank(),
                   strip.text.y = element_text(face = "bold")))
  }
}

@@

#binned probability cell count for the whole 3d space per month

```{r}
library(stringr)

#calculate no of cells in the 3D space
prob <- read.csv("../output/maxent/paper_plots/prob_by_depth/apr_dis_prob_cells.csv", header = TRUE) #just a randomly chosen dataset
t2 <- subset(prob, Probability == "0 - 0.09") #could have chosen any probability
tc <- sum(t2$total_cells) #173623

dislst <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "dis_prob_cells.csv", full.names = TRUE)
totlst <- list()
for (m in 1:length(dislst)){
  pr <- read.csv(dislst[m])
  mth <- str_sub(dislst[m], start = 44, end = 46)
  pr2 <- aggregate(pr$Cells, by=list(Category = pr$Probability), FUN = sum)
  pr2$percent <- (pr2$x/tc)*100
  pr2$month <- mth
  write.csv(pr2, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_cellprob_totals.csv"), row.names = FALSE)
  totlst[[m]] <- pr2
}

#then i just made a table manually in excel
```

#max kappa thresholds

```{r}
binprob <- function(x){
  ifelse(x > 0 & x >= mk, 1,
  ifelse(x <= 0, 0, NA))
}

alst <- list.files("../output/maxent/models/test-comb/", pattern = "avgAIC.csv", full.names = TRUE)

for (f in 1:length(alst)){
  mth <- str_sub(alst[f], start = 35, end = 37)
  af <- read.csv(alst[f], header = TRUE)
  af <- tail(af, n = 1)
  mk <- af$test_maxkap

  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}

get data to plot probability by depth... 
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_maxkap.*asc"), full.names = TRUE)
  binaryavgstack <- stack(ascdepth)
  stackstathigh <- data.frame(matrix(ncol = 2, nrow = nlayers(binaryavgstack)))
  stackstathigh[ ,1] <- c(1:47)
  colnames(stackstathigh) <- c("asclayer", "prob_bin")

  for (lyr in 1:nlayers(binaryavgstack)){
    ascname <-  str_sub(ascdepth[lyr], 67, -5)
    dlay <- binaryavgstack[[lyr]]
    dlay <- calc(dlay, fun = binprob) #creates raster layer with cell values based on the binprob function
    lyrsum <- cellStats(dlay, sum)
    stackstathigh$prob_bin[lyr] <- lyrsum
    stackstathigh$asclayer[lyr] <- ascname

  }
  write.csv(stackstathigh, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

from here sam

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  probblst <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_probbin_.*.csv"), full.names = TRUE)
  a <- read.csv(probblst[1])
  b <- read.csv(probblst[2])
  c <- read.csv(probblst[3])
  d <- read.csv(probblst[4])
  e <- read.csv(probblst[5])
  f <- read.csv(probblst[6])
  g <- read.csv(probblst[7])
  h <- read.csv(probblst[8])
  i <- read.csv(probblst[9])
  j <- read.csv(probblst[10])

  write.csv(stackstat, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_allprobbin_cellcount_bydepth_avg.csv"), row.names = FALSE)
}
